Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2018-12-11 tex/WW4C_VHzQ.tex
tex/WW4C_VHzQ updated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%  S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%  S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
%%trim=l b r t
%  \includegraphics[width=18.6cm, clip,trim=14mm 4mm 10mm 10mm]
  \includegraphics[width=8.6cm, clip,trim=32mm 4mm 32mm 10mm]
  {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/filters_vs_QSOstars_20180704.pdf}
  \centering
  \vspace{-12pt}
  \caption[]
  {The spectral bands used by different survey telescopes and that are relevant here.
    The $grizy$ filters are from the Pan-STARRS survey. The $JHK$ are from 
    UKIRT/WFCAM, while $K_{s}$ is a VISTA/VIRCAM filter. The 
    The narrow W-band centered at $\lambda\approx14,500$\AA\ is a CFHT/Wircam filter. 
    [NJC: Do we use the W-band anywhere?]
    The WISE passbands  W1-4 are also presented.
    The quasar spectrum is a composite based on \citet{VdB2001} and 
    \citet{Banados2016}. The L and T dwarf spectra are from \citet{Cushing2006}. 
  }
  \label{fig:filters}
\end{figure}

@@

\subsection{MIR data}
The MIR data for this study comes exclusively from the Wide-field
Infrared Survey Explorer (WISE) mission. Since we are only concerned
here with the very large area ($\gg1000$ deg$^2$) surveys, we leave
exploration of the VH$z$Q population in e.g. the large Spitzer areal
surveys such as the Spitzer IRAC Equatorial Survey \citep[SpIES;
][]{Timlin2016}, the Spitzer-HETDEX Exploratory Large-area Survey
\citep[SHELA; ][]{Papovich2016} and the Spitzer-SPT Deep Field
\citep[SSDF; ][]{Ashby2013}, to a future investigation. This will also
include a detailed study of MIR spectra e.g. \citet{Lambrides2018}.

We use data from the the beginning of the WISE mission \citep[2010
January; ][]{Wright2010} through the fourth-year of NEOWISE-R
operations \citep[2017 December;]{Mainzer2011}. More specifically, we
use the data from the
\href{http://wise2.ipac.caltech.edu/docs/release/allwise/}{AllWISE}
program and catalogue, which combines data from the WISE cryogenic and
NEOWISE (Mainzer et al. 2011 ApJ, 731, 53) post-cryogenic survey
phases. For the our variability investigations, we supplement the
ALLWISE data with data from the
\href{http://wise2.ipac.caltech.edu/docs/release/neowise/neowise_2018_release_intro.html}{NEOWISE
2018 Data Release}. NEOWISE 2018 makes available the 3.4 and 4.6 μm
(W1 and W2) single-exposure images and extracted source information
that were acquired between 2016 December 13 and 2017 December 13 UTC,
which was the fourth year of survey operations of the Near-Earth
Object Wide-field Infrared Survey Explorer Reactivation Mission
(NEOWISE; Mainzer et al. 2014, ApJ, 792, 30). The fourth year NEOWISE
data products are concatenated with those from the first three years
(originally released on March 26, 2015, March 23, 2016 and June 1,
2017) into a single archive.

The WISE scan pattern leads to coverage of the full- sky approximately
once every six months (a``sky pass''), but the satellite was placed in
hibernation in 2011 February and then reactivated in 2013
October. Hence, our light curves have a cadence of 6 months with a 32
month sampling gap.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%  S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%  S E C T I O  N   2         S E C T I O  N   2           S E C T I O  N   2       S E C T I O  N   2
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
%%trim=l b r t
%  \includegraphics[width=18.6cm, clip,trim=14mm 4mm 10mm 10mm]
  \includegraphics[width=8.6cm, clip,trim=32mm 4mm 32mm 10mm]
  {/cos_pc19a_npr/programs/quasars/highest_z/SEDs/filters_vs_QSOstars_z7pnt0.pdf}
  \centering
  \vspace{-12pt}
  \caption[]
  {The spectral bands used by different survey telescopes and that are relevant here.
    The $grizy$ filters are from the Pan-STARRS survey. The $JHK$ are from 
    UKIRT/WFCAM, while $K_{s}$ is a VISTA/VIRCAM filter. The 
    The narrow W-band centered at $\lambda\approx14,500$\AA\ is a CFHT/Wircam filter. 
    [NJC: Do we use the W-band anywhere?]
    The WISE passbands  W1-4 are also presented.
    The quasar spectrum is a composite based on \citet{VdB2001} and 
    \citet{Banados2016}. The L and T dwarf spectra are from \citet{Cushing2006}. 
  }
  \label{fig:filters}
\end{figure}

@@

\subsection{MIR data}
Since we are concerned here with the very large area ($\gg1000$ deg$^2$) surveys, we leave exploration of the VH$z$Q population in e.g. the large Spitzer areal surveys such as the Spitzer IRAC Equatorial Survey \citep[SpIES; ][]{Timlin2016}, the Spitzer-HETDEX Exploratory Large-area Survey \citep[SHELA; ][]{Papovich2016} and the Spitzer-SPT Deep Field \citep[SSDF; ][]{Ashby2013}, to future investigation. This will also include a detailed study of MIR spectra e.g. \citet{Lambrides2018}.

The MIR data for this study comes exclusively from the Wide-field Infrared Survey Explorer (WISE) mission. 
\href{http://wise2.ipac.caltech.edu/docs/release/allwise/}{AllWISE}
program and catalogue, which combines data from the WISE cryogenic and
NEOWISE (Mainzer et al. 2011 ApJ, 731, 53) post-cryogenic survey
phases. For the our variability investigations, we supplement the
ALLWISE data with data from the
\href{http://wise2.ipac.caltech.edu/docs/release/neowise/neowise_2018_release_intro.html}{NEOWISE
2018 Data Release}. NEOWISE 2018 makes available the 3.4 and 4.6 μm
(W1 and W2) single-exposure images and extracted source information
that were acquired between 2016 December 13 and 2017 December 13 UTC,
which was the fourth year of survey operations of the Near-Earth
Object Wide-field Infrared Survey Explorer Reactivation Mission
(NEOWISE; Mainzer et al. 2014, ApJ, 792, 30). The fourth year NEOWISE
data products are concatenated with those from the first three years
(originally released on March 26, 2015, March 23, 2016 and June 1,
2017) into a single archive.

We use data from the the beginning of the WISE mission \citep[2010 January; ][]{Wright2010} through the fourth-year of NEOWISE-R operations \citep[2017 December;]{Mainzer2011}.  More specifically, we utilise the recently released ``unWISE Catalog'' \citet{MeisnerSchlafly2019}. The unWISE effort\footnote{http://unwise.me/} is the unblurred coadds of the WISE imaging using the AllWISE and NEOWISE-R stacked data \citep{Lang2014, Meisner2018a, Meisner2018b}. {\bf Few more words here on the unWISE catalog}.

All fluxes in the unWISE catalog are reported there are in ``Vega nanoMaggies'', with the Vega magnitude of a source is given by $m_{\rm Vega} = 22.5−2.5\log(f)$, where $f$ is the source flux. The absolute calibration for unWISE is ultimately inherited from AllWISE through the calibration of \citet{Meisner2017}. This inheritance depends on details of the PSF normalization at large radii, which is uncertain. Subtracting 4 mmag from the unWISE W1, and 32 mmag from unWISE W2 fluxes improves the agreement between unWISE and AllWISE fluxes.

Thus to convert unWISE Vega magnitudes onto the AB system, we have,   
\begin{eqnarray*}
        W1_{\rm AB, unWISE}  & = &   22.5 - 2.5 \log(f_{W1}) - 0.004 + 2.699 \\
        W2_{\rm AB, unWISE}  &  = &  22.5 - 2.5 \log(f_{W2}) - 0.032 + 3.339 
\end{eqnarray*}
%those two numbers are how far our flux measurements differed on average from the AllWISE flux estimates at high Galactic latitudes.  These tweaks will move you closer to the AllWISE absolute calibration, which we haven't tried to improve upon.
%We note though that 
%Especially in W1, though, this correction is uncertain, because the average offset between AllWISE and unWISE depends on magnitude, and we don't really know
%- what the source of the trend is,
%- which of unWISE and AllWISE is correct, or
%- where the AllWISE tie to AB/Vega was done (though presumably it was done on the bright end?).

The WISE scan pattern leads to coverage of the full-sky approximately once every six months (a``sky pass''), but the satellite was placed in hibernation in 2011 February and then reactivated in 2013 October. Hence, our light curves have a cadence of 6 months with a 32 month sampling gap.
